Uncertainty propagation in neural networks for sparse coding

### 2018-11-29 nips_workshop_2018/camera_ready/BayesianLISTA.tex
minor

   \begin{figure}[!t]
  \centering
  \subfloat[Synthetic for different $L$]{\includegraphics[width=0.25\textwidth]{graphics/synthetic_number_of_layers/nmse_validation}
  \label{fig:nmse_n_layers_synthetic}}
  \hfil
  \subfloat[Synthetic for different $K$]{\includegraphics[width=0.25\textwidth]{graphics/synthetic_undersampling/nmse_validation}
  \label{fig:nmse_undersampling_synthetic}}
  \hfil
  \subfloat[Active learning example]{\includegraphics[width=0.25\textwidth]{graphics/active_mnist/nmse_validation}
  \label{fig:active_learning_mnist}}
  \caption{NMSE results. The synthetic data results for different number of layers~\protect\subref{fig:nmse_n_layers_synthetic} and for different sizes of observations~\protect\subref{fig:nmse_undersampling_synthetic}. The active learning example results on the MNIST data~\protect\subref{fig:active_learning_mnist}.}
  \label{fig:number_of_layers_synthetic}
  \end{figure}

>>>>

   \begin{figure}[!t]
  \centering
  \subfloat[Synthetic for different $L$]{\includegraphics[width=0.28\textwidth]{graphics/synthetic_number_of_layers/nmse_validation}
  \label{fig:nmse_n_layers_synthetic}}
  \hfil
  \subfloat[Synthetic for different $K$]{\includegraphics[width=0.28\textwidth]{graphics/synthetic_undersampling/nmse_validation}
  \label{fig:nmse_undersampling_synthetic}}
  \hfil
  \subfloat[Active learning example]{\includegraphics[width=0.28\textwidth]{graphics/active_mnist/nmse_validation}
  \label{fig:active_learning_mnist}}
  \caption{NMSE results. The synthetic data results for different number of layers~\protect\subref{fig:nmse_n_layers_synthetic} and for different sizes of observations~\protect\subref{fig:nmse_undersampling_synthetic}. The active learning example results on the MNIST data~\protect\subref{fig:active_learning_mnist}.}
  \label{fig:number_of_layers_synthetic}
  \end{figure}
